Incentivizing Exploration by Heterogeneous Users

### 2018-02-09 appendix.tex
edited the payment, regret and lower bound proof

\[ \Prob{\text{play a new arm}|\mathcal{F}_t} =
\begin{cases}
1       & \quad \text{if we incentivize}\\
\sum_{i\in V} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{otherwise}  
\end{cases} \label{dom_stoc}
\] 
\hspace{1cm}$\geq (n-|V|)\times \frac{1}{n}=1-\frac{|V|}{n}$.
\bccomment{Wait for Peter to address this}

Let $(Z_{s,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $(1-\frac{v}{s})$. We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
\begin{align}
t_{s}-t_{s-1}\leq \bar{T}_{s}:=\sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}, \nonumber 
\end{align}
where $\bar{T}_{s,v}:=\inf\{m\geq 0: Z_{s,v,m}=1\}+1$.

The new stochastic process will have the property that whenever $Z_{s,v(s,t),m(s,t)}=1$, we will play a new arm at time t for $t\in [t_{s-1}, t_{s}]$, where $v(s,t)$ is the number of unique arms played in phase $s$ strictly before time $t$, and $m(s,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(s,t)$. At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} and let $q_t$ be the probability computed. Note $q_t\geq 1-\frac{v(s,t)}{s}$.

@@

\begin{align}
\Prob{\text{play a new arm}|\mathcal{F}_{t}}=\left[1-\frac{v(s,t)}{s}\right]+\left[1-(1-\frac{v(s,t)}{s})\right]\times \frac{q_t-(1-\frac{v(s,t)}{s})}{1-(1-\frac{v(s,t)}{s})}=q_t.
\end{align}

@@

Set $g(s,\ell)$ to be $\frac{12\sigma \ell}{s^{2/5}}$. Since if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\AgV\in \{\AgV:\AgV\cdot \ArmV{\Best{\AgV}}-\AgV \cdot \ArmV{\Second{\AgV}}> 2\Diam d\lambda\}$, they will correctly identify their best arm. Thus, if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \frac{12\sigma l}{s^{2/5}} \leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a phase $s$ that satisfies $s^{-1}\leq \MinProb/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{24\Diam d\sigma}{p^{-1}(\frac{\MinProb}{2})}$. In order to have $\frac{12\sigma l}{s^{2/5}}\leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$, it is sufficient to have $s\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$. In order to have $s^{-1}\leq \frac{\MinProb}{2}$, we need $s\geq \frac{2}{\MinProb}$. Denote $s_2=\frac{2}{\MinProb}$. Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ phases.

@@

Thus,
\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
\leq&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\omega\in L[\ell])E[\bar{T}_{s}} \nonumber \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\Prob{\omega\in L[1]}E[\bar{T}_{s}] +\sum_{l=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\omega\in L[\ell]}E[\bar{T}_{s}] \nonumber \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]E[\bar{T}_{s}] +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1)^2}E[\bar{T}_{s}]\nonumber \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\ARMNUM s +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24 \ARMNUM d e^{-1.8(\ell-1)^2}\ARMNUM s \nonumber \\
\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM (\max\{s_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma](\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1)^2} \nonumber \\
=& O(\frac{N}{\MinProb^5}+ \frac{\ARMNUM^2}{\MinProb^5}). \nonumber
\end{align}

\section*{Calculation for Equation~\eqref{ex:limit}}

In this section, we prove $d(t)\leq \frac{z_{t,1}^{2}}{2}$ and $\lim_{t\rightarrow\infty}d(t)=\frac{z_{t,1}^2}{2}$. Denote $w(x)=\sqrt{x}$. Then we know $w(x+y)\leq \sqrt{x} + y\frac{1}{2\sqrt{x}}$ and $w(x+y)\geq \sqrt{x} + y\frac{1}{2\sqrt{x+y}}$ for $y\geq 0$. Thus, we know

\begin{align}
&\lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right] \nonumber \\
=& \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
\geq & \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{t}+z_{t,2}+z_{t,1}^{2}\frac{1}{2\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
= & \lim_{t\rightarrow\infty} t \times \frac{z_{t,1}^2}{2(z_{t,1}^2+(\sqrt{t}+z_{t,2})^2)} \rightarrow \frac{z_{t,1}^2}{2}. \nonumber 
\end{align}
and
\begin{align}
&\lim_{t\rightarrow\infty} t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right] \nonumber \\
=& \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
\leq & \lim_{t\rightarrow\infty} t\left[\frac{\sqrt{t}+z_{t,2}+z_{t,1}^{2}\frac{1}{2\sqrt{(\sqrt{t}+z_{t,2})^2}}-\sqrt{t}-z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]  \nonumber \\
= & \lim_{t\rightarrow\infty} t \times \frac{z_{t,1}^2}{2\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}(\sqrt{t}+z_{t,2})} \rightarrow \frac{z_{t,1}^2}{2}. \label{inequ:dct}
\end{align}   
Based on inequality~\eqref{inequ:dct}, we know $d(t)\leq \frac{z_{t,1}^{2}}{2}$ and $\lim_{t\rightarrow\infty}d(t)=\frac{z_{t,1}^2}{2}$.

>>>>

\[ \Prob{\text{play a new arm}|\mathcal{F}_t} =
\begin{cases}
1       & \quad \text{if we incentivize}\\
\sum_{i\in V} P(\AgentV{t} \cdot \ArmEV{t}{i}>\AgentV{t}\cdot \ArmEV{t}{j} \forall j\neq i)  & \quad \text{otherwise}  
\end{cases} \label{dom_stoc}
\] 
\hspace{1cm}$\geq (\ARMNUM-|V_t|)\times \frac{1}{\log(s)}$.
\bccomment{probably we need to be more careful about $\frac{1}{\log(s)}$}.
Let $(Z_{s,v,m}:m\geq 0)$ be a sequence of independent Bernoulli random variable with success probability $\frac{\ARMNUM-v}{\log(s)}$. We will construct an alternative stochastic process for selecting which arm gets played that has the same distribution as the original process, but under which
\begin{align}
t_{s}-t_{s-1}\leq \bar{T}_{s}:=\sum_{v=0}^{\ARMNUM-1}\bar{T}_{s,v}, \nonumber 
\end{align}
where $\bar{T}_{s,v}:=\inf\{m\geq 0: Z_{s,v,m}=1\}+1$.

The new stochastic process will have the property that whenever $Z_{s,v(s,t),m(s,t)}=1$, we will play a new arm at time t for $t\in [t_{s-1}, t_{s}]$, where $v(s,t)$ is the number of unique arms played in phase $s$ strictly before time $t$, and $m(s,t)$ is the number of times we have pulled a previously pulled arm for the current value of $v(s,t)$. At time $t$, to determine what arm to pull, calculate \eqref{dom_stoc} \bccomment{why this eqref does not work properly? }and let $q_t$ be the probability computed. Note $q_t\geq \frac{\ARMNUM-v(s,t)}{\log(s)}$.

@@

\begin{align}
\Prob{\text{play a new arm}|\mathcal{F}_{t}}=\frac{\ARMNUM-v}{\log(s)}+\left[1-\frac{\ARMNUM-v}{\log(s)}\right]\times \frac{q_t-\frac{\ARMNUM-v}{\log(s)}}{1-\frac{\ARMNUM-v}{\log(s)}}=q_t.
\end{align}

@@

Set $g(s,\ell)$ to be $\frac{12\sigma \ell}{s^{2/5}}$. Since if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \lambda$ is true $\forall i$, $\forall j$, then we know for those $\AgV\in \{\AgV:\AgV\cdot \ArmV{\Best{\AgV}}-\AgV \cdot \ArmV{\Second{\AgV}}> 2\Diam d\lambda\}$, they will correctly identify their best arm. Thus, if $|\Arm{i}{j}-\ArmE{t}{i}{j}|\leq \frac{12\sigma l}{s^{2/5}} \leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$ $\forall i$ and $\forall j$, then the probability that an unincentivized agent would pull arm $i$ is at least $\frac{p}{2}$. Further, if time $t$ is in a phase $s$ that satisfies $1/log(s)\leq \MinProb/2$, then our algorithm will not incentivize pulling any arms. Denote $a_0=\frac{24\Diam d\sigma}{p^{-1}(\frac{\MinProb}{2})}$. In order to have $\frac{12\sigma l}{s^{2/5}}\leq \frac{p^{-1}(\frac{\MinProb}{2})}{2\Diam d}$, it is sufficient to have $s\geq \lceil (a_{0} l)^\frac{5}{2} \rceil$. In order to have $1/\log(s)\leq \frac{\MinProb}{2}$, we need $s\geq \exp(\frac{2}{\MinProb})$. Denote $s_2=\exp(\frac{2}{\MinProb})$. Thus, we know we can only incur regret for sample paths $\omega$ in the $\ell^{th}$ envelope in the first $\max\{s_2,\lceil (a_0 \ell)^\frac{5}{2} \rceil\}$ phases.

@@

Thus,
\begin{align}
&\sum_{t=1}^{\infty}c(t) \nonumber \\
\leq&\sum_{\ell=1}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\omega\in L[\ell])E[\bar{T}_{s}} \nonumber \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\Prob{\omega\in L[1]}E[\bar{T}_{s}] +\sum_{l=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]\Prob{\omega\in L[\ell]}E[\bar{T}_{s}] \nonumber \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[R+24\Diam d\sigma \right]E[\bar{T}_{s}] +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24\ARMNUM d e^{-1.8(\ell-1)^2}E[\bar{T}_{s}]\nonumber \\
\leq& \sum_{s=1}^{\max\{s_2,\lceil (a_0)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \right]\ARMNUM \log(s) +\sum_{\ell=2}^{\infty}\sum_{s=1}^{\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\}}\left[\MAXR+24\Diam d\sigma \ell\right]24 \ARMNUM d e^{-1.8(\ell-1)^2}\ARMNUM \log(s) \nonumber \\
\leq & \left[\MAXR+24\Diam d\sigma \right]\ARMNUM (\max\{s_2,\lceil (a_0)^{5/2} \rceil\})^2+\sum_{\ell=2}^{\infty}24\ARMNUM^2 d[\MAXR+24\Diam d\ell\sigma](\max\{s_2,\lceil (a_0 \ell)^{5/2} \rceil\})^2 e^{-1.8(\ell-1)^2} \nonumber \\
=& O(\max\{\frac{\ARMNUM^2}{\MinProb^5},\ARMNUM^2\exp(\frac{4}{\MinProb})\}). \nonumber
\end{align}

\bccomment{in the second to last inequality, I use $s\leq \log(s)$, probably a very loose bound.}
\end{proof}

### 2018-02-09 lower_bound.tex
editted the lower bound
edited the payment, regret and lower bound proof

@@

Given $z_{t,1}>0$ and $z_{t,2}>0$, we know users whose preference vector between $(-1,0)$ and $\left(\frac{-1-z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ as well as users whose preference vector between $(1,0)$ and $\left(\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}, \frac{-z_{t,1}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right)$ will make a mistake. The regret is the absolute value of the second coordinate of the user's preference vector. Thus, we know

\begin{align}
&E[r(t)| z_{t,1}>0, z_{t,2}>0] \nonumber \\
=& 4\times 2 \int_{0}^{\infty} \int_{0}^{\infty} \int_{0}^{\arctan\left(\frac{z_{t,1}}{1+z_{t,2}}\right)}\frac{\sin(\theta)}{2\pi}d(\theta)\frac{e^{-\frac{t \times z_{t,1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,1})\frac{e^{-\frac{t \times z_{t,2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(z_{t,2}) \nonumber \\
=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}t\times \left[1-\frac{1+z_{t,2}}{\sqrt{z_{t,1}^2+(1+z_{t,2})^2}}\right]e^{-\frac{t \times z_{t,1}^2}{2}}e^{-\frac{t \times z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}) \nonumber \\
=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty} \left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}d(z_{t,1})d(z_{t,2}). \nonumber 
\end{align}

Below, we want to show 
\begin{align}
\lim_{t\rightarrow\infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} = O(1), \nonumber
\end{align}
and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$.

Denote $d(t)=t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]$. Based on our calculation (see appendix for details), we know $d(t)\leq \frac{z_{t,1}^2}{2}$ and

\begin{align}
\lim_{t\rightarrow \infty} d(t)=\frac{z_{t,1}^2}{2}. \label{ex:limit}
\end{align}
Based on the dominated convergence theorem, we know
\begin{align}
&\lim_{t\rightarrow \infty}\frac{E[r(t)| z_{t,1}>0, z_{t,2}>0]}{\frac{1}{t}} \nonumber \\
=& \frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t\left[1-\frac{\sqrt{t}+z_{t,2}}{\sqrt{z_{t,1}^2+(\sqrt{t}+z_{t,2})^2}}\right]e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) \nonumber  \\
=&\frac{2}{\pi^2}\int_{0}^{\infty} \int_{0}^{\infty}\left[ \frac{z_{t,1}^2}{2}e^{-\frac{z_{t,1}^2}{2}}e^{-\frac{z_{t,2}^2}{2}}\right]d(z_{t,1})d(z_{t,2}) = \frac{1}{2\pi}. \nonumber
\end{align}

Thus, the cumulative expected regret is at least $\Omega(\log(T))$.

>>>>

\begin{align}
&E[r(t)| \Noise{1}>0, \Noise{2}>0] \nonumber \\
\geq & 4\times \frac{1}{3\pi} \int_{0}^{\infty} \int_{0}^{\infty} (\frac{\Noise{1}}{1+\Noise{1}+\Noise{2}})^2\frac{e^{-\frac{t \times \Noise{1}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(\Noise{1})\frac{e^{-\frac{t \times \Noise{2}^2}{2}}\sqrt{t}}{\sqrt{2\pi}}d(\Noise{2}) \nonumber \\
= & \frac{1}{3\pi^3} \int_{0}^{\infty} \int_{0}^{\infty} (\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2e^{-\frac{\Noise{1}^2}{2}}d(\Noise{1})e^{-\frac{\Noise{2}^2}{2}}d(\Noise{2}) \nonumber 
\end{align}

Below, we want to show 
\begin{align}
\lim_{t\rightarrow\infty}\frac{E[r(t)| \Noise{1}>0, \Noise{2}>0]}{\frac{1}{t}} = \Omega(1), \nonumber
\end{align}
and use the fact that $\sum_{n=1}^{T}\frac{1}{n}=O(\log(T))$ to show the regret is at least $\Omega(\log(T))$. Since
\begin{align}
&\lim_{t\rightarrow \infty}\frac{E[r(t)| \Noise{1}>0, \Noise{2}>0]}{\frac{1}{t}} \nonumber \\
\geq & \lim_{t\rightarrow \infty}\frac{1}{3\pi^3}\int_{0}^{\infty} \int_{0}^{\infty}\left[ t(\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2\right]e^{-\frac{\Noise{1}^2}{2}}e^{-\frac{\Noise{2}^2}{2}}d(\Noise{1})d(\Noise{2}) \nonumber  \\
= & \frac{1}{3\pi^3}\int_{0}^{\infty} \int_{0}^{\infty}\lim_{t\rightarrow \infty}\left[ t(\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2\right]e^{-\frac{\Noise{1}^2}{2}}e^{-\frac{\Noise{2}^2}{2}}d(\Noise{1})d(\Noise{2}) \nonumber  \\
=&\frac{1}{3\pi^3}\int_{0}^{\infty} \int_{0}^{\infty}e^{-\frac{\Noise{1}^2}{2}}e^{-\frac{\Noise{2}^2}{2}}d(\Noise{1})d(\Noise{2}) = \frac{1}{3\pi^3}, \nonumber
\end{align}

where the third line is due to monotone convergence theorem since the derivative of $t(\frac{\Noise{1}}{\sqrt{t}+\Noise{1}+\Noise{2}})^2$ is greater than $0$.

@@
